Review: Redefining Domestication: Adaptive Introgression during Crop Expansion

### 2017-06-16 paper.tex
Update paper.tex

>>>>

http://biology.unm.edu/Whitney/Whitney%20Reprints/Whitney%20et%20al.%202006%20Am%20Nat.pdf

http://www.jstor.org/stable/pdf/2409227.pdf?refreqid=excelsior:a686b7f06f9daa2b89bd5a654dade3b4

file:///home/gjanzen/Downloads/Whitney_et_al-2010-New_Phytologist%20(2).pdf

http://onlinelibrary.wiley.com/doi/10.1111/j.1469-8137.2010.03234.x/epdf

https://biology.unm.edu/Whitney/Whitney%20Reprints/Scascitelli%20et%20al%202010.pdf
